supplements_webcamcoding

### 2022-05-20 stats/analysis.Rmd
change naming of model comparison tables

```{r extvali_save}
extvali_results <- mExtvaliComparison %>%
  left_join(mExtvaliComparisonWeights) %>%
  select(model, waic, value, elpd_diff, se_diff) %>%
  rename(
    Predictor = model, 
    WAIC = waic, 
    Weight = value, 
    ELPD = elpd_diff, 
    SE = se_diff,
  ) %>% 
  mutate(
    Predictor = recode(Predictor, 
                   "mExtvaliPE" = "Peer exposure index", 
                   "mExtvalisiblingsVarietyScoreW" = "Sibling variety score (Cassidy et al., 2005)", 
                   "mExtvalihhSibs" = "# Children in household aged 0-18", 
                   "mExtvaliccHours" = "Average hours spent in childcare per day",
                   "mExtvalinull" = "Null model", 
                   "mExtvalihhTotal" = "# Household members",
                   "mExtvaliccAge" = "Age of childcare entry", 
                   "mExtvalisiblingsVarietyScoreP" = "Sibling variety score (Peterson, 2000)", 
                   "mExtvalisibsChildAged" = "# Children in household aged 1-12",
                   )
  )

@@

```{r extvali_plot}
ggplot(extvali_draws, aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
 tidybayes::stat_halfeye(alpha = .7, .width = c(.95, .80), scale = 3) +
    labs(x = "Posterior estimate", y = "")+
  guides(fill = "none")+
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_fill_manual(values = c("grey","#85AD00")) +
  xlim(-0.2, 0.6) +
  theme_minimal()

>>>>

```{r extvali_save}
extvali_results <- mExtvaliComparison %>%
  left_join(mExtvaliComparisonWeights) %>%
  select(model, waic, se_waic, value, elpd_diff, se_diff) %>%
  rename(
    Predictor = model, 
    WAIC = waic, 
    SE_WAIC = se_waic,
    Weight = value, 
    ELPD_DIFF = elpd_diff, 
    SE_ELPD_DIFF = se_diff,
  ) %>% 
  mutate(
    Predictor = recode(Predictor, 
                   "mExtvaliPE" = "Peer exposure index", 
                   "mExtvalisiblingsVarietyScoreW" = "Sibling variety score (Cassidy et al., 2005)", 
                   "mExtvalihhSibs" = "# Children in household aged 0-18", 
                   "mExtvaliccHours" = "Average hours spent in childcare per day",
                   "mExtvalinull" = "Null model", 
                   "mExtvalihhTotal" = "# Household members",
                   "mExtvaliccAge" = "Age of childcare entry", 
                   "mExtvalisiblingsVarietyScoreP" = "Sibling variety score (Peterson, 2000)", 
                   "mExtvalisibsChildAged" = "# Children in household aged 1-12",
                   )
  )

@@

```{r extvali_plot}
ggplot(extvali_draws, aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
 tidybayes::stat_halfeye(alpha = .8, .width = c(.95, .80), scale = 3) +
    labs(x = "Posterior estimate", y = "")+
  guides(fill = "none")+
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_fill_manual(values = c("grey","#85AD00")) +
  xlim(-0.2, 0.6) +
  theme_minimal()

ggsave("../figures/extvali_results_all.png", width = 10, height = 6, scale = 0.7, bg = "white")

### 2022-05-20 stats/supplements_webcamcoding.Rmd
change naming of model comparison tables

```{r overall_save}
overall_results <- bind_rows(mPerTrialComparison, mPerSubjectComparison) %>% 
  left_join(bind_rows(mPerTrialComparisonWeights, mPerSubjectComparisonWeights)) %>% 
  select(model, waic, value, elpd_diff, se_diff) %>% 
  rename(
    Predictor = model, 
    WAIC = waic, 
    Weight = value, 
    ELPD = elpd_diff, 
    SE = se_diff,
  ) %>% 
  mutate(
    Predictor = recode(Predictor, 
                   "mPerTrialVerificationChoice" = "By trial - # Verification choice", 
                   "mPerTrialNull" = "By trial - Null model", 
                   "mPerTrialPI" = "By trial - Parental interference index", 
                   "mPerTrialRepeatedTestquestion" = "By trial - # Repeated testquestion", 
                   "mPerTrialParentSpeech" = "By trial - # Words uttered by caregiver", 
                   "mPerTrialHintsEyes" = "By trial - # Hints eyes", 
                   "mPerSubjectRepeatedTestquestion" = "By subject - # Repeated testquestion", 
                   "mPerSubjectPI" = "By subject - Parental interference index", 
                   "mPerSubjectNull" = "By subject - Null model", 
                   "mPerSubjectVerificationChoice" = "By subject - # Verification choice", 
                   "mPerSubjectParentSpeech" = "By subject - # Words uttered by caregiver", 
                   "mPerSubjectHintsEyes" = "By subject - # Hints eyes"
                   )
  )

>>>>

```{r overall_save}
overall_results <- bind_rows(mPerTrialComparison, mPerSubjectComparison) %>% 
  left_join(bind_rows(mPerTrialComparisonWeights, mPerSubjectComparisonWeights)) %>% 
  select(model, waic, se_waic, value, elpd_diff, se_diff) %>% 
  rename(
    Predictor = model, 
    WAIC = waic, 
    SE_WAIC = se_waic,
    Weight = value, 
    ELPD_DIFF = elpd_diff, 
    SE_ELPD_DIFF = se_diff,
  ) %>% 
  mutate(
    Predictor = recode(Predictor, 
                   "mPerTrialVerificationChoice" = "By trial - # Verification choice", 
                   "mPerTrialNull" = "By trial - Null model", 
                   "mPerTrialPI" = "By trial - Parental interference index", 
                   "mPerTrialRepeatedTestquestion" = "By trial - # Repeated testquestion", 
                   "mPerTrialParentSpeech" = "By trial - # Words uttered by caregiver", 
                   "mPerTrialHintsEyes" = "By trial - # Hints eyes", 
                   "mPerSubjectRepeatedTestquestion" = "By subject - # Repeated testquestion", 
                   "mPerSubjectPI" = "By subject - Parental interference index", 
                   "mPerSubjectNull" = "By subject - Null model", 
                   "mPerSubjectVerificationChoice" = "By subject - # Verification choice", 
                   "mPerSubjectParentSpeech" = "By subject - # Words uttered by caregiver", 
                   "mPerSubjectHintsEyes" = "By subject - # Hints eyes"
                   )
  )
